Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
more on Alessandro's comments

We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs\footnote{Notice that since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable.}.
%, which may restrict the observability of the state-space from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}. 
\end{equation}
%
Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
time~\cite{middleton1990digital,van1978computing} at constant intervals, whose 
duration we refer to as the sample time $T_s$, 
into the difference equation 
\begin{align}
\label{eq:plant}
\left\{
\begin{array}{rl}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
\end{array}
\right.
\text{ where }
\left\{
\begin{array}{l}
\mat{A}_d=e^\mat{A}\\
\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
\end{array}
\right.,
\end{align} 
%
\note{Ad is ill defined?}
%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
In this work we raise the standard assumption that $\mat{D}=\mat{0}$ \cite{Astrom08}.  
%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{State observers}\label{sec:observer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

In many models of real-world control systems, 
the internal state $x$ cannot be directly measured,  
but is rather inferred from its effect on the measured output $\vec{y}$ using an observer~\cite{Astrom08}.  
Essentially, a state observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$) 
that provides an estimate of the internal state $x$ of the given model, 
from measurements of its inputs and outputs \note{(see Appendix~\ref{sec:observable})}.

A closed-loop digital control interconnection with observer is shown in Figure~\ref{fig:observersystem}. 
The linear feedback controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
and is driven by the observer state $\hat{\vec{x}}$.  
Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error on the output estimator,  
%  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.
Note that the controller and the observer are implemented in a discrete domain 
(quantities within this domain are identified by the index $\langle C \rangle$), 
whereas the plant evolves in a continuous domain. 
We further model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
$\nu_2'$ (rounding of the observer state), and $\nu_t$ (output delay of the digital system) 
  Lastly, $k_r$ is a reference gain required by the model.

  Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
  so that specific closed-loop properties of the overall interconnection are satisfied.

@@

@@

%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
We assume that the system has no inputs, so its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

 \begin{lemma}
 The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
 evaluated at time $T$ is
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn2}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$. 
 \end{lemma}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Next, we are interested in studying models with parametric inputs, 
 which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
 For such models, a state $\vec{x}_T$ is computed next.  \note{The next result is again known from literature, it's not a new theorem.}
\begin{theorem}
The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
 \end{align}
 where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}\footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
 then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
 \end{corollary}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

@@

The final case we analyse is that of hybrid-time models, 
where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time.  
A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
%
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, 
 and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
%  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}, 
 and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
 is the state of the model 
 \begin{align}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s. 
 \end{align}
 \end{theorem}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

@@

Stability qualitatively denotes the property of a model to evolve within a bounded set around an equilibrium point. 
In this paper, we are interested in asymptotic stability, where the model is further expected to converge to the steady state value (i.e., the equilibrium point).   
%
We specify model stability via Jury's criterion~\cite{fadali}, 
as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
 which boils down to a requirement expressed as an algebraic formula 
 on the characteristic polynomial of the model - a SAT solver will manipulate its coefficients. 
%
In order to facilitate the use of Jury's criterion, we transform the model into
a representation that contains the coefficients of its characteristic
polynomial expressed as sums of controller and plant values. 
The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers. 
%
Such a representation is a model known as 
% is called Controllable and Observable 
``canonical form''~\cite{Astrom08} %\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
and is dynamically equivalent to the given model.  
In this section we explore the implications of using the canonical form, 
alongside the use of FWL representations.

@@

We assume that the domain of the observer model is discretised, 
i.e., the domain for both the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
This means that we have matrices 
${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},\mat{C}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$, 
where $*$ represents the appropriate dimension for each matrix.
New problems arise due to FWL effects on these matrices. 
These are reflected in the canonical form of the resulting model,
which is expressed by:
%
{\setlength{\belowdisplayskip}{2pt}
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right], %\nonumber\\
%\vec{y}_k= &\mat{C}\mat{T}_c\vec{x}_k', 
% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
}
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_c=&\left[\begin{array}{cc}
\begin{array}{ccc}k_{p-1}-a_{p-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
\mat{I}&\begin{array}{c}0\\ \vdots \\ 0\end{array}
\end{array}\right]&
\mat{A}_o=&\left[\begin{array}{cc}
\begin{array}{c}l_{p-1}-a_{p-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
\end{array}\right], 
\end{align*}
}
where $\vec{x}'$ is the state of the model in canonical form and $\vec{x}_e'$ is the error of the observer evaluated in the transformed domain; 
further, $\mat{A}_{c}$ the closed-loop matrix of the controller in canonical form, 
$\mat{A}_{o}$ the closed-loop matrix of the observer in canonical form, 
$\mat{B}_{o}$ the a feedback gain matrix, 
 $\mat{B}'$ the noise sensitivity matrix, 
\note{[next is unclear - how are matrices related to FWL errors? are they related to the quantities discussed in the previous section 5.2?] and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL representation}.
%and we have introduced the following terms: 
%{\setlength{\abovedisplayskip}{2pt}
%\setlength{\belowdisplayskip}{2pt}
%\begin{align*}
%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
%\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
%\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
%\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
%\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
%\mat{C}_{e}=&\mat{C}-\mat{C}_{\langle C \rangle}
%\end{align*}
%}
%{\setlength{\abovedisplayskip}{0pt}
%\begin{align*}
%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
%\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
%\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2',
%\end{align*}
%}
Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (details are in Appendix~\ref{sec:quantization-noise}).

In a continuous time domain, the characteristic polynomial
of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
and~$\mat{A}_o$.  
\begin{align*}
P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
\end{align*}
The introduction of the FWL errors causes this to no longer
be true.  We must therefore find a suitable solution to maintain this separation of polynomials.

>>>>

We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs\footnote{Notice that since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable.}.
%, which may restrict the observability of the state-space from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}. 
\end{equation}
%
Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
time~\cite{middleton1990digital,van1978computing} at constant intervals, whose 
duration we refer to as the sample time $T_s$, 
into the difference equation 
\begin{align}
\label{eq:plant}
\left\{
\begin{array}{rl}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
\end{array}
\right.
\text{ where }
\left\{
\begin{array}{l}
\mat{A}_d=e^{\mat{A}T_s}\\
\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
\end{array}
\right.,
\end{align} 
%
%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
In this work we raise the standard assumption that $\mat{D}=\mat{0}$ \cite{Astrom08}.  
%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{State observers}\label{sec:observer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In many models of real-world control systems, 
the internal state $x$ cannot be directly measured,  
but is rather inferred from its effect on the measured output $\vec{y}$ using an observer~\cite{Astrom08}.  
Essentially, a state observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$) 
that provides an estimate of the internal state $x$ of the given model, 
from measurements of its inputs and outputs.

A closed-loop digital control interconnection with observer is shown in Figure~\ref{fig:observersystem}. 
The linear feedback controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
and is driven by the observer state $\hat{\vec{x}}$.  
Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error on the output estimator,  
%  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.
Note that the controller and the observer are implemented in a discrete domain 
(quantities within this domain are identified by the index $\langle C \rangle$), 
whereas the plant evolves in a continuous domain. 
We further model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
$\nu_2'$ (rounding of the observer state), and $\nu_t$ (output delay of the digital system) 
Lastly, $k_r$ is a reference gain required by the model.  
Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
 so that specific closed-loop properties of the overall interconnection are satisfied.

@@

\note{Much like we did in the earlier work, we should emphasise we look at the closed-loop interconnection from the perspective of the digital controller? }

@@

%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
We assume that the system has no inputs, so its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

 \begin{lemma}
 The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
 evaluated at time $T$ is
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn2}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$. 
 \end{lemma}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Next, we are interested in studying models with parametric inputs, 
 which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
 For such models, a state $\vec{x}_T$ is computed next.
\begin{lemma}
The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
 \label{eq:continuous_tube_param}
 \end{align}
 where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
 \footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
 then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
 \end{lemma}

@@

The final case we analyse is that of hybrid-time models, 
where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time.  
A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
%
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in \eqref{eq:continuous_tube_param}, 
 and $\mat{A}_d=\mat{A}_{T_s}, \mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with sample time $T_s$, 
 is the state of the model 
 \begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s. 
 \end{align*}
 \end{theorem}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

@@

Stability qualitatively denotes the property of a model to evolve within a bounded set around an equilibrium point. 
In this paper, we are interested in asymptotic stability, where the model is further expected to converge to the steady state value (i.e., the equilibrium point).   
%
We specify model stability via Jury's criterion~\cite{fadali}, 
as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
 which boils down to a requirement expressed as an algebraic formula 
 on the characteristic polynomial of the model - a SAT solver will manipulate its coefficients. 
 \note{unclear really how SAT relates to manipulating real coefficients.... }
%
In order to facilitate the use of Jury's criterion, we transform the model into
a representation that contains the coefficients of its characteristic
polynomial expressed as sums of controller and plant values. 
The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers. 
%
Such a representation is a model known as 
% is called Controllable and Observable 
``canonical form''~\cite{Astrom08} %\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
and is dynamically equivalent to the given model.  
In this section we explore the implications of using the canonical form, 
alongside the use of FWL representations.

@@

We assume that the domain of the observer model is discretised, 
i.e., the domain for both the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
This means that we have matrices 
${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},\mat{C}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$, 
where $*$ represents the appropriate dimension for each matrix.
New problems arise due to the FWL truncation of these matrices. 
These are reflected in the canonical form of the resulting model (see $\mat{A}_e$ and $\mat{B}_e$),
which is expressed by:
%
{\setlength{\belowdisplayskip}{2pt}
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right], %\nonumber\\
%\vec{y}_k= &\mat{C}\mat{T}_c\vec{x}_k', 
% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
}
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_c=&\left[\begin{array}{cc}
\begin{array}{ccc}k_{p-1}-a_{p-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
\mat{I}&\begin{array}{c}0\\ \vdots \\ 0\end{array}
\end{array}\right]&
\mat{A}_o=&\left[\begin{array}{cc}
\begin{array}{c}l_{p-1}-a_{p-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
\end{array}\right], 
\end{align*}
}
where $\vec{x}'$ is the state of the model in canonical form and $\vec{x}_e'$ is the error of the observer evaluated in the transformed domain; 
further, $\mat{A}_{c}$ the closed-loop matrix of the controller in canonical form, 
$\mat{A}_{o}$ the closed-loop matrix of the observer in canonical form, 
$\mat{B}_{o}$ the a feedback gain matrix, 
 $\mat{B}'$ the noise sensitivity matrix, 
and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL truncation, seen after the transformation to canonical form.
%and we have introduced the following terms: 
%{\setlength{\abovedisplayskip}{2pt}
%\setlength{\belowdisplayskip}{2pt}
%\begin{align*}
%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
%\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
%\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
%\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
%\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
%\mat{C}_{e}=&\mat{C}-\mat{C}_{\langle C \rangle}
%\end{align*}
%}
%{\setlength{\abovedisplayskip}{0pt}
%\begin{align*}
%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
%\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
%\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2',
%\end{align*}
%}
Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \note{[How is this related to the previously mentioned FWL errors?]} Full details are in Appendix~\ref{sec:quantization-noise}.

In a real domain $\mathbb{R}$, the characteristic polynomial
of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
and~$\mat{A}_o$.  
\begin{align*}
P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
\end{align*}
\note{we should perhaps provide a qualitative hint on what are the conditions of JC? I'm afraid leaving it to the polynomials here isn't quite complete or clear.}
The introduction of the FWL errors causes this to no longer
be true.  We must therefore find a suitable solution to maintain this independence of polynomials.
